The imprint of global magma oceans on exoplanet demographics

### 2023-03-11 src/tex/ms.tex
swap detection bias and measurements

\subsection{Measurements and their uncertainties}
Under real-world conditions, the planetary properties in question can only be probed with a finite precision that is specific to each exoplanet mission.
%\subsubsection{PLATO}
\plato\ (PLAnetary Transits and Oscillation of stars) is an ESA mission designed to characterize terrestrial planets in the habitable zones of Sun-like stars, a goal to be achieved via long-term high-precision photometric monitoring of a sample of bright stars~\citep{Rauer2016}.
\plato's definition study report~\citep{plato2017} states precision requirements for planet radii~(\SI{3}{\percent}), planet masses through radial velocity~(RV) follow-up~(\SI{10}{\percent}), and stellar masses, radii, and ages~(\SI{10}{\percent}).
We adopted these estimates and assumed a \SI{10}{\percent} error on instellation measurements.

@@

A successful transit detection requires a sufficient signal-to-noise ratio (S/N), which is sensitive on the achieved photometric precision. %~\citep[e.g.,][]{Koch2010,Ricker2014,Burke2015,Hardegree-Ullman2019} % Cabrera+ in prep for PLATO
%In its in-orbit commissioning phase, the \cheops\ mission demonstrated a photometric precision of \SI{75}{\ppm} for faint ($V\approx 12$) stars~\citep{Benz2021}.
%In comparison, \plato's expected precision for similar stars was estimated to be \SI{\sim 50}{\ppm}~\citep[][Matuszewski et al., in prep.]{plato2017}.
In line with its requirement to detect Earth-sized planets in a \SI{1}{\year} orbit around Sun-like stars, \plato\ is designed to enable the detection of a \SI{80}{\ppm} transit signal~\citep[][Matuszewski et al., in prep.]{plato2017}.
To reflect its sensitivity, we chose a minimum transit depth of \SI{80}{\ppm} as a detection limit and consider only measurements of planets exceeding this threshold.
We further exclude target stars with \gaia\ magnitudes $M_\mathrm{G} > \minMagnitude$.

>>>>

A successful transit detection requires a sufficient signal-to-noise ratio (S/N), which is sensitive on the achieved photometric precision. %~\citep[e.g.,][]{Koch2010,Ricker2014,Burke2015,Hardegree-Ullman2019} % Cabrera+ in prep for PLATO
%In its in-orbit commissioning phase, the \cheops\ mission demonstrated a photometric precision of \SI{75}{\ppm} for faint ($V\approx 12$) stars~\citep{Benz2021}.
%In comparison, \plato's expected precision for similar stars was estimated to be \SI{\sim 50}{\ppm}~\citep[][Matuszewski et al., in prep.]{plato2017}.
\plato\ (PLAnetary Transits and Oscillation of stars) is an ESA mission designed to characterize terrestrial planets in the habitable zones of Sun-like stars, a goal to be achieved via long-term high-precision photometric monitoring of a sample of bright stars~\citep{Rauer2016}.
In line with this requirement, \plato\ is designed to enable the detection of a \SI{80}{\ppm} transit signal~\citep[][Matuszewski et al., in prep.]{plato2017}.
To reflect its sensitivity, we chose a minimum transit depth of \SI{80}{\ppm} as a detection limit and consider only measurements of planets exceeding this threshold.
We further exclude target stars with \gaia\ magnitudes $M_\mathrm{G} > \minMagnitude$.

\subsection{Measurements and their uncertainties}
Under real-world conditions, the planetary properties in question can only be probed with a finite precision that is specific to each exoplanet mission.
%\subsubsection{PLATO}
\plato's definition study report~\citep{plato2017} states precision requirements for planet radii~(\SI{3}{\percent}), planet masses through radial velocity~(RV) follow-up~(\SI{10}{\percent}), and stellar masses, radii, and ages~(\SI{10}{\percent}).
We adopted these estimates and assumed a \SI{10}{\percent} error on instellation measurements.

@@
